---
title: Scatter Plots
author: Georgie Warren
date: '2017-12-12'
slug: scatter-plots
categories:
  - R
tags:
  - scatterplot
  - sql
---

Welcome back to my Data Science blog! Today, we will be disussing Scatter Plots. We are going to be extracting data from a database of baseball statistics in order to demostarte how to make a Scatter Plot. Remember, you must always begin by installing the necessary packages into RStudio and subsequently bringing them in with Library(). This includes Lahman, sqldf and ggplot2. 

```{r warning= FALSE, message= FALSE}
library(Lahman)
library(sqldf)
library(ggplot2)
```

Now, lets take a look at this query I have below! As you can see, I am narrowing all the information down within the baseball database in order to find career homeruns and strikeouts from players who had 400 or more homeruns. 

```{r}
query<-"SELECT playerID,sum(HR),sum(SO)
FROM Batting
GROUP BY playerID
HAVING sum(HR)>400"

sqldf(query)
```

Don't forget to save it as a result!

```{r}
query<-"SELECT playerID,sum(HR) AS CareerHR,sum(SO) AS CareerSO
FROM Batting
GROUP BY playerID
HAVING sum(HR)>400"

result<-sqldf(query)
```

Now that we finished collecting and organizing the data we need, it's time to make it into a Scatter Plot! We're going to make the X axis Career Strikeouts and the Y axis Career Homeruns. Make sure to include a title, in this case, it will be "Career Strikeouts and Homeruns"

```{r}
ggplot()+
  geom_point(data=result,aes(x=CareerSO,y=CareerHR),size=3)+
  ggtitle("Career Strikeouts and Homeruns")+
  xlab("Career Strikeouts")+
  ylab("Career Homeruns")
```

We just successfully completed our first Scatter Plot! Easy right? 
