---
title: Histograms
author: Georgie Warren
date: '2017-12-12'
slug: histograms
categories:
  - R
tags:
  - histogram
  - sql
---

Welcome back to my Data Science blog! Today we are going to be having a lesson on histograms! Just like with all of our previous lessons, we need to download all of our packages and bring them in through library.

Below, are all of the packages that we need!

```{r warning= FALSE, message= FALSE}
library(Lahman)
library(sqldf)
library(ggplot2)
```

This is query that we need in order to get the data on the weights of baseball players.

```{r}
query<-"SELECT weight FROM Master"
result<-sqldf(query)
```

Now, using ggplot, we can personalize our histogram by changing the colors, bins and labels! Very important! 

```{r}
ggplot()+
  geom_histogram(data=result,aes(x=weight),color="blue",fill="white",bins=60)+
  ggtitle("Distribution of Baseball Player Bodyweight")+
  xlab("Weight of player")+
  ylab("Number of players")
```

As you can see, histograms are very similar to scatter plots! Although, there are a few commands that are necessary for histograms.

```{r}
ggplot()+
  geom_histogram(data=result,aes(x=weight),color="blue",fill="white",bins=10)+
  ggtitle("Distribution of Baseball Player Bodyweight")+
  xlab("Weight of player")+
  ylab("Number of players")
```

As a way to help y'all visualize the importance of bin numbers, above I only have 10 bins and below I changed that number to 100!

```{r}
ggplot()+
  geom_histogram(data=result,aes(x=weight),color="blue",fill="white",bins=100)+
  ggtitle("Distribution of Baseball Player Bodyweight")+
  xlab("Weight of player")+
  ylab("Number of players")
```

Nice job everyone, we just successfully make a histogram!! More to come, next time we will look into how to make a bar plot!
