---
title: Bar Plots
author: Georgie Warren
date: '2017-12-12'
slug: bar-plots
categories:
  - R
tags:
  - bar plot
  - sql
---

Welcome back to my Data Science blog! In this lesson today we are going to dicuss how to make a bar plot! As always, we need to download all of our necessary packages and bring them in through library, as shown below!

```{r warning= FALSE, message= FALSE}
library(Lahman)
library(sqldf)
library(ggplot2)
```

This is the query that we need in order to get the data on total homeruns for MLB teams in 1980!

```{r}
query<-"SELECT name,HR FROM Teams WHERE yearID=1980 ORDER BY HR "
result<-sqldf(query)

result$name<-factor(result$name,levels=result$name)
```

Now it's time to add our own personal touch to our bar plot! Lets give it a title with labels on the X and Y axis!

```{r}
ggplot()+
  geom_bar(data=result,aes(x=name,y=HR),stat='identity')+
  coord_flip()+
  ggtitle("1980 Team Homerun Totals")+
  xlab("Team Name")+
  ylab("Homeruns")
```

Make sure to look at the above example and see how we strategically flipped the X and Y axis on the graph in order to get the proper output of data! 

Nice job everyone, we just made our very own bar plot!!