---
title: Time Series
author: Georgie Warren
date: '2017-12-12'
slug: time-series
categories:
  - R
tags:
  - time series
  - sql
---

Welcome to my first lesson on Data Science! Today we are going to be learning about how to make a Time Series! The very first (and extremely important) step that we need to take is to download all of our packages and bring them in through library. In this case, that includes: Lahman, sqldf and ggplot2.

```{r warning= FALSE, message= FALSE}
library(Lahman)
library(sqldf)
library(ggplot2)
```

Again, we are going to be using the baseball database in order to make the Time Series. However, for this example we are going to be specifically using data about one specific player, Babe Ruth. Below, is the query needed to extract the data we need. 

```{r}
query<-"SELECT yearID,HR FROM Batting WHERE playerID='ruthba01'"

sqldf(query)
```

Don't forget to save it as a result!

```{r}
query<-"SELECT yearID,HR FROM Batting WHERE playerID='ruthba01'"

result<-sqldf(query)
```

Next, lets make that into a Time Series! The X axis will be "Year" and the Y axis will be "Number of Homeruns". Make sure to name it as well, in this case it will be "Babe Ruth's Homeruns by Year"

```{r}
ggplot()+
  geom_point(data=result,aes(x=yearID,y=HR),size=1/2)+
  geom_line(data=result,aes(x=yearID,y=HR))+
  ggtitle("Babe Ruth's Homeruns by Year")+
  xlab("Year")+
  ylab("Number of Homeruns")
```

We just successfully completed our first Time Series!